Parallel Global Search Algorithm with Local Tuning\\ for Solving Mixed-Integer Global Optimization Problems

### 2021-02-18 2021/Lobachevskii_BarkalovLebedev/ljmsamp.tex
fix some misprints

\firstcollaboration{(Submitted by A.~A.~Editor-name)} % Add if you know submitter.
%\lastcollaboration{ }

\received{February 1, 2021} % The date of receipt to the editor, i.e. December 06, 2017

@@

An extensive literature is devoted to methods for solving mixed-integer problems (see, for example, reviews \cite{Burer,Boukouvala}). Known deterministic methods for solving problems of this class are based, as a rule, on the Branch-and-Bound \cite{Belotti} or Branch-and-Reduce \cite{Vigerske}. . Such problems may also be solved by nature-inspired algorithms \cite{Deep,Schluter}, which in one way or another are based on a random search.

@@

Within this approach 
\begin{itemize}
	\item 
	solving multidimensional problems is reduced to solving equivalent one-dimensional problems, the corresponding reduction is based on the use of space-filling curves;
	\item 
	when solving constrained optimization problems, each constraint is taken into account and processed separately, and penalty functions are not used;
	\item
	taking into account the information on the inhomogeneous behavior of the problem functions in different subdomains of the search domain makes it possible to speed up the process of finding a solution by combining the procedures for local refinement of the current best solution and its global update;
	\item 
	parallelization of the search process is carried out by simultaneous calculation of several values of the objective function at different points of the search domain during each iteration.	
\end{itemize}

@@

Let us consider a parallel algorithm for solving constrained global optimization problems proposed in  \cite{Strongin2000,Strongin2013} and based on an index scheme for the accounting of constraints.

To describe a parallel algorithm, we will assume that we have $p$ computational elements (nodes, processors, or cores) at our disposal, which will be used for parallel execution of $p$ trials simultaneously.

@@

\begin{enumerate}
\item 
Renumber the points $x^1,...,x^k$ of the previous trials with subscripts in ascending order of coordinate values
\begin{equation}\label{Eq:17}
0=x_0<x_1<...<x_i<...<x_k<x_{k+1}=1,
\end{equation}
and assign $z_i=g_\nu(y(x_i))$, $\nu=\nu(x_i)$, $1 \leq i \leq k$; points $x_0=0$ and $x_{k+1}=1$ are introduced additionally, values $z_0$ and $z_{k+1}$ are not set.
\item
Classify indexes  $i,1\leq i \leq k$, of the trial points from  (\ref{Eq:17}) by the number of constraints that are met at these points by constructing the sets
\begin{equation}\label{Eq:18}
I_\nu = \left\{i: 1 \leq i \leq k,\ \nu = \nu(x_i)\right\},\ 1 \leq \nu \leq m+1,
\end{equation}
containing the indices of all points $x_i,1\leq i \leq k$, with indices equal to the same value $\nu$. The boundary points $x_0=0$ and $x_{k+1}=1$ are interpreted as having zero indices, and an additional set $I_0={0,k+1}$ is assigned to them.

Determine the maximum value of indices
\begin{equation}\label{Eq:19}
V=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values  
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, j<i\right\}.
\end{equation}
If set $I_\nu$ contains less than two elements or if $\mu_\nu$ from (\ref{Eq:20}) is equal to zero, then use the value $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, calculate values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =  
   \begin{cases}
    -\epsilon_\nu,  \nu < V, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = V,
   \end{cases}
\end{equation}
where $V$ is the maximum index value and the vector
\begin{equation}\label{Eq:22}
\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right),
\end{equation}
with positive components (also referred to as \textit{reserve vector}) is the algorithm parameter.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristics} $R(i)$: 
\begin{eqnarray}\label{R}
&R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),\nonumber \\
&R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,\\
&R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i),\nonumber
\end{eqnarray}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and values $r_\nu>1, 1\leq\nu\leq m+1$, are the algorithm parameters.
\item
Sort characteristics $R(i)$, $1\leq i \leq k+1$, in descending order 	
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and select $p$ intervals with numbers $t_j, 1\leq j \leq p,$ corresponding to the largest characteristics.
\item
Conduct $p$ new trials in parallel at points $x^{k+j}, 1 \leq j \leq p$, calculated by the formulas
\begin{eqnarray*}
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}), \\
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \; \nu(x_{t_j-1})=\nu(x_{t_j})=\nu. \\
\end{eqnarray*}

@@

In accordance with this approach, it is possible to construct adaptive forecasting rules based on the assumption that the location of the global optimum is more likely to lie in the vicinity of the points from the series $x_i, 1 \leq i \leq k,$ which correspond to small values of the normalized differences $\omega_i=(z_i-z_\nu^*)/\mu_\nu$, where $\mu_\nu$ is from (\ref{Eq:20}), and $z_\nu^*$ is from  (\ref{Eq:21}).

This hypothesis is plausible either in the case when the number of performed iterations is large enough (since the algorithm, when the convergence conditions are satisfied, generates a sequence of trials that is dense only at the points of the global minimum), or in the case when the problem is unimodal (i.e. when the search in the vicinity of the best current approximation allows for improvement, and such successive improvements lead to a solution). The first case corresponds to the final phase of the search, and then the use of adaptive forecast can be interpreted as a way to speed up the refinement of the solution. While, the second case actually includes assumptions about the weak multiextremity of the problem.

@@

Let us now consider the case when the argument of the problem functions contains two components: vector $y$, which belongs to the hyperinterval $D$, and vector $u$, which has a finite (and not very large) set of possible values, i.e.
\begin{eqnarray}\label{problem_i}
& \min{\left\{ g_{m+1}(y,u):y\in D, \; g_i(y,u)\leq 0, \; 1 \leq i \leq m\right\}},\\
& D=\left\{a_j\leq y_j \leq b_j, \; 1\leq j \leq N \right\}.\nonumber
\end{eqnarray}

@@

Let us assign integers  $s, 1\leq s \leq S,$ to all possible values of the vector $u$, i.e. associate each considered value $s$ with a vector $u_s$. 
Then the problem can be written as
\begin{eqnarray}\label{problem_is}
& \min_{s\in\{1,...,S\}}\left(\min{\left\{ g_{m+1}(y,u_s):y\in D, \; g_i(y,u_s)\leq 0, \; 1 \leq i \leq m\right\}}\right),\\
& D=\left\{ a_j\leq y_j \leq b_j, \; 1 \leq j\leq N \right\}.\nonumber 
\end{eqnarray}

@@

To illustrate this, Fig. \ref{fig:1} shows graphs of functions corresponding to a problem with one continuous and one binary parameter.
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{fig1.jpg}
    \caption{Mixed-integer global optimization problem}
    \label{fig:1}
\end{figure}

@@

The first series of experiments was carried out using a sequential version of the algorithm without using local tuning in order to compare it with other similar methods.

The PMGAL algorithm proposed in this work (in its sequential version) was compared with the genetic algorithm for solving mixed-integer optimization problems implemented in the Matlab Global Optimization Toolbox. Table \ref{tab:1} shows the number of trials it took for these methods to solve a number of mixed-integer test problems taken from \cite{Deep,Floudas}. The same accuracy of search $10^{-2}$ was used for both methods. All computational experiments were carried out on a computer with an Intel Core i5-7300 2.5 GHz processor and 8 Gb RAM. The experimental results show the superiority of the PMGAL method both in terms of the number of iterations and the running time.

\begin{table}
	\caption{Comparison of the effectiveness of the PMGAL and GA methods}
	\label{tab:1}
	\center
	\begin{tabular}{|c|c|c|c|c|}
		\hline
	\multirow{2}{*}{Test problem}	 & \multicolumn{2}{c|}{ GA } &  \multicolumn{2}{c|}{MIGSA} \\
		\cline{2-3} \cline{4-5} 
		 & $k$ & $t$ &  $k$ & $t$  \\
		\hline 
		 Problem 2 \cite{Floudas}&	481 &	0.0601 & 	417 &	0.04 \\
		 Problem 6 \cite{Floudas}&	641 &	0.0510 & 	118 &	0.001 \\
		 Problem 1 \cite{Deep}   &	481 &	0.1378 & 	66 &	0.0007 \\
		 Problem 2 \cite{Deep}   &	481 &	0.0473 & 	57 &	0.0006 \\
		 Problem 7 \cite{Deep}   &	841 &	0.0736 &  372	 &	0.017 \\
		\hline
	\end{tabular}
\end{table}

The next experiment was conducted to assess the effect of local tuning on accelerating the convergence of the algorithm. We used the GKLS generator \cite{Gaviano} to generate test problems of continuous multiextremal optimization. GKLS allows generating continuous functions of a given dimensionality with specific properties: a known number of local minima, a known domain of attraction of the global solution, etc.  
%This generator of multiextremal functions is often used for the investigations of the global optimization algorithms \cite{Paulavicius2014,SergeyevKvasov2015,Lebedev2015,Gergel2015}.

Fig.~\ref{example} (a) and (b) shows the contour plots of two-dimensional GKLS functions. These figures also shows the points of the trials performed by the global search until the required accuracy $\epsilon=10^{-2}$ was achieved.

\begin{figure}
\begin{minipage}{0.48\linewidth}
\center{\includegraphics[width=1.0\linewidth]{GKLS-4.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.48\linewidth}
\center{\includegraphics[width=1.0\linewidth]{GKLS-6.png} \\ (b)}
\end{minipage}
\caption{Solving a two-dimensional problem using the global search algorithm}
\label{example}
\end{figure}

@@

\begin{enumerate}
	\item GKLS generates a continuous multiextremal function $\psi(y), \; y\in D, \; D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\}$. The global minimum of this function is achieved at the known point $y'=(y'_1,...,y'_N)$ and is equal to $\psi'=\psi(y')=-1$.
	\item A convex mixed-integer function
	\[
			\phi (y,u) = 2 \left[ \sum_{j=1}^N \left( \frac{y_j - y'_j}{b_j-a_j} \right)^2 + \sum_{j=1}^M \left( \frac{u_j - b_j}{b_j-a_j} \right)^2 \right]
	\]
	is generated, where 
	\begin{eqnarray*}
	& y\in D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\} \subset R^N, \\
	& u\in U = \left\{ u_j \in  \left\{a_j, ..., b_j \right\}, 1\leq j \leq M \right\};
	\end{eqnarray*}
	i.e. this function has $N$ continuous and $M$ discrete parameters and reaches its minimum value at the point $(y',b)$.
	\item The coefficient is calculated
	\[
	C = 4 - \max_{y,u} \left\{ \phi(y,u) \right\}, \; y\in D, u \in U.
	\]
	The maximum of the convex function $\phi(y,u)$ is achieved at one of the boundary points of the search domain; therefore, when the dimensionality of the problem is around 10, its calculation can be performed by the enumeration method. 
	\item  Multi-extreme mixed-integer function is formed
	\[
	\varphi(y,u) = \left(\psi(y) - \sum_{j=1}^M{u_j}\right)\left(C - \phi(y,u)\right).
	\]
	By construction, $\varphi(y,u)$ will reach the minimum value at the point $(y',b)$.

@@

The problems generated in our experiments had 5 discrete and 4 continuous parameters 
	\begin{eqnarray*}
	& y\in D = \left\{ -1 \leq y_j\leq 1, 1\leq j \leq 4 \right\} \subset R^4, \\
	& u\in U = \left\{ u_j \in  \left\{-1, -1/3, 1/3, 1 \right\}, 1\leq j \leq 4 \right\}.
	\end{eqnarray*}

In total, we generated and solved 100 9-dimensional mixed-integer problems of this type. In order to simulate the computational complexity inherent in applied optimization problems, the calculation of the function in all the experiments was complicated by additional calculations that did not change the form of the function and the location of its minima.
The accuracy of the search was equal to $10^{-2}$. Computational experiments were carried out on the Lobachevsky supercomputer. The node of supercomputer included two Intel Sandy Bridge E5-2660 2.2 GHz CPUs and 64 Gb RAM.

@@

\begin{table}
	\caption{Average running time $T_{av}$ of the parallel algorithm with a local tuning}
	\label{tab:3}
	\center
	\begin{tabular}{|c|c|c|c|}
		\hline	
	\diaghead{\theadfont Diag Column} { $N_{p}$}{$N_{t}$} & 1 & 4 & 8\\

>>>>

\firstcollaboration{(Submitted by V.~V.~Voevodin)} % Add if you know submitter.
%\lastcollaboration{ }

\received{February 20, 2021} % The date of receipt to the editor, i.e. December 06, 2017

@@

An extensive literature is devoted to methods for solving mixed-integer problems (see, for example, reviews \cite{Burer,Boukouvala}). Known deterministic methods for solving problems of this class are based, as a rule, on the Branch-and-Bound \cite{Belotti} or Branch-and-Reduce approach \cite{Vigerske}. Such problems may also be solved by nature-inspired algorithms \cite{Deep,Schluter}, which in one way or another are based on a random search.

@@

Within this approach: 
\begin{itemize}
	\item 
	solving multidimensional problems is reduced to solving equivalent one-dimensional problems, the corresponding reduction is based on the use of space-filling curves;
	\item 
	when solving constrained optimization problems, each constraint is taken into account and processed separately, and penalty functions are not used;
	\item
	taking into account the information on the inhomogeneous behavior of the problem functions in different subdomains of the search domain makes it possible to speed up the process of finding a solution by combining the procedures for local refinement of the current best solution and its global update;
	\item 
	parallelization of the search process is carried out by simultaneous calculation of several values of the objective function at different points of the search domain during each iteration.	
\end{itemize}

@@

Let us consider a parallel algorithm for solving constrained global optimization problems proposed in  \cite{Strongin2000,Strongin2013} and based on an index scheme for the accounting of constraints.
To describe a parallel algorithm, we will assume that we have $p$ computational elements (nodes, processors, or cores) at our disposal, which will be used for parallel execution of $p$ trials simultaneously.

@@

\begin{enumerate}
\item 
Renumber the points $x^1,...,x^k$ of the previous trials with subscripts in ascending order of coordinate values
\begin{equation}\label{Eq:17}
0=x_0<x_1<...<x_i<...<x_k<x_{k+1}=1,
\end{equation}
and assign $z_i=g_\nu(y(x_i))$, $\nu=\nu(x_i)$, $1 \leq i \leq k$; points $x_0=0$ and $x_{k+1}=1$ are introduced additionally, values $z_0$ and $z_{k+1}$ are not set.
\item
Classify indexes  $i,1\leq i \leq k$, of the trial points from  (\ref{Eq:17}) by the number of constraints that are met at these points by constructing the sets
\begin{equation}\label{Eq:18}
I_\nu = \left\{i: 1 \leq i \leq k,\ \nu = \nu(x_i)\right\},\ 1 \leq \nu \leq m+1,
\end{equation}
containing the indices of all points $x_i,1\leq i \leq k$, with indices equal to the same value $\nu$. The boundary points $x_0=0$ and $x_{k+1}=1$ are interpreted as having zero indices, and an additional set $I_0=\{0,k+1\}$ is assigned to them.

Determine the maximum value of indices
\begin{equation}\label{Eq:19}
V=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values  
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, j<i\right\}.
\end{equation}
If set $I_\nu$ contains less than two elements or if $\mu_\nu$ from (\ref{Eq:20}) is equal to zero, then use the value $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, calculate values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =  
   \begin{cases}
    -\epsilon_\nu,  \nu < V, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = V,
   \end{cases}
\end{equation}
where $V$ is the maximum index value and the vector
\begin{equation}\label{Eq:22}
\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right),
\end{equation}
with positive components (also referred to as \textit{reserve vector}) is the algorithm parameter.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristics} $R(i)$: 
\begin{eqnarray}\label{R}
&R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),\nonumber \\
&R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,\\
&R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i),\nonumber
\end{eqnarray}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and values $r_\nu>1, 1\leq\nu\leq m+1$, are the algorithm parameters.
\item
Sort characteristics $R(i)$, $1\leq i \leq k+1$, in descending order 	
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and select $p$ intervals with numbers $t_j, 1\leq j \leq p,$ corresponding to the largest characteristics.
\item
Conduct $p$ new trials in parallel at points $x^{k+j}, 1 \leq j \leq p$, calculated by the formulas
\begin{gather*}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}), \\
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \; \nu(x_{t_j-1})=\nu(x_{t_j})=\nu. \\
\end{gather*}

@@

In accordance with this approach, it is possible to construct adaptive forecasting rules based on the assumption that the location of the global optimum is more likely to lie in the vicinity of the points from the series $x_i, 1 \leq i \leq k,$ from (\ref{Eq:17}), which correspond to small values of the normalized differences $\omega_i=(z_i-z_\nu^*)/\mu_\nu$, where $\mu_\nu$ is from (\ref{Eq:20}), and $z_\nu^*$ is from  (\ref{Eq:21}).

This hypothesis is plausible either in the case when the number of performed iterations is large enough (since the algorithm, when the convergence conditions are satisfied, generates a sequence of trials that is dense only at the points of the global minimum), or in the case when the problem is unimodal (i.e. when the search in the vicinity of the current best point allows for improvement, and such successive improvements lead to a solution). The first case corresponds to the final phase of the search, and then the use of adaptive forecast can be interpreted as a way to speed up the refinement of the solution. While, the second case actually includes assumptions about the weak multiextremity of the problem.

@@

Let us now consider the case when the argument of the problem functions contains two components: vector $y$, which belongs to the hyperinterval $D$, and vector $u$, which has a finite (and not very large) set of possible values $U$, i.e.
\begin{eqnarray}\label{problem_i}
& \min{\left\{ g_{m+1}(y,u):y\in D, u \in U, \; g_i(y,u)\leq 0, \; 1 \leq i \leq m\right\}},\\
& D=\left\{a_j\leq y_j \leq b_j, \; 1\leq j \leq N \right\}.\nonumber
\end{eqnarray}

@@

Let us assign integers  $s, 1\leq s \leq S,$ to all possible values of the vector $u$, i.e. associate each considered value $s$ with a vector $u_s$. 
Then the problem can be written as
\begin{gather}\label{problem_is}
 \min_{s\in\{1,...,S\}}\left\{\min{\left\{ g_{m+1}(y,u_s):y\in D, \; g_i(y,u_s)\leq 0, \; 1 \leq i \leq m\right\}}\right\},\\
 D=\left\{ a_j\leq y_j \leq b_j, \; 1 \leq j\leq N \right\}.\nonumber 
\end{gather}

@@

To illustrate this, Fig. \ref{fig:1} shows graphs of functions corresponding to a problem with one continuous and one binary parameter.
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{fig1.jpg}
    \caption{Mixed-integer global optimization problem}
    \label{fig:1}
\end{figure}

@@

The first series of experiments was carried out using a sequential version of the algorithm without using local tuning in order to compare it with other similar methods.
The PMGAL algorithm proposed in this work (in its sequential version) was compared with the genetic algorithm for solving mixed-integer optimization problems implemented in the Matlab Global Optimization Toolbox. Table \ref{tab:1} shows the number of trials it took for these methods to solve a number of mixed-integer test problems taken from \cite{Deep,Floudas}. The same accuracy of search $\epsilon = 10^{-2}$ was used for both methods. All computational experiments were carried out on a computer with an Intel Core i5-7300 2.5 GHz processor and 8 Gb RAM. The experimental results show the superiority of the PMGAL method both in terms of the number of iterations and the running time.

\begin{table}[ht]
	\caption{Comparison of the effectiveness of the PMGAL and GA methods}
	\label{tab:1}
	\center
	\begin{tabular}{|c|c|c|c|c|}
		\hline
	\multirow{2}{*}{Test problem}	 & \multicolumn{2}{c|}{ GA } &  \multicolumn{2}{c|}{PMGAL} \\
		\cline{2-3} \cline{4-5} 
		 & $k$ & $t$ &  $k$ & $t$  \\
		\hline 
		 Problem 2 \cite{Floudas}&	481 &	0.0601 & 	417 &	0.04 \\
		 Problem 6 \cite{Floudas}&	641 &	0.0510 & 	118 &	0.001 \\
		 Problem 1 \cite{Deep}   &	481 &	0.1378 & 	66 &	0.0007 \\
		 Problem 2 \cite{Deep}   &	481 &	0.0473 & 	57 &	0.0006 \\
		 Problem 7 \cite{Deep}   &	841 &	0.0736 &  372	 &	0.017 \\
		\hline
	\end{tabular}
\end{table}

The next experiment was conducted to assess the effect of local tuning on accelerating the convergence of the algorithm. We used the GKLS generator \cite{Gaviano} to generate test problems of continuous multiextremal optimization. GKLS allows generating continuous functions of a given dimensionality with specific properties: a known number of local minima, a known domain of attraction of the global solution, etc.  
%This generator of multiextremal functions is often used for the investigations of the global optimization algorithms \cite{Paulavicius2014,SergeyevKvasov2015,Lebedev2015,Gergel2015}. 
Fig.~\ref{example} (a) and (b) shows the contour plots of two-dimensional GKLS functions. These figures also shows the points of the trials performed by the global search until the required accuracy $\epsilon=10^{-2}$ was achieved.

\begin{figure}
\begin{minipage}{0.48\linewidth}
\center{\includegraphics[width=1.0\linewidth]{GKLS-4.png} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.475\linewidth}
\center{\includegraphics[width=1.0\linewidth]{GKLS-6.png} \\ (b)}
\end{minipage}
\caption{Solving a two-dimensional problem using the global search algorithm}
\label{example}
\end{figure}

@@

\begin{enumerate}
	\item GKLS generates a continuous multiextremal function $\psi(y), \; y\in D, \; D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\}$. The global minimum of this function is achieved at the known point $y'=(y'_1,...,y'_N)$ and is equal to $\psi'=\psi(y')=-1$.
	\item A convex mixed-integer function
	\[
			\phi (y,u) = 2 \left[ \sum_{j=1}^N \left( \frac{y_j - y'_j}{b_j-a_j} \right)^2 + \sum_{j=1}^M \left( \frac{u_j - b_j}{b_j-a_j} \right)^2 \right]
	\]
	is generated, where 
	\begin{eqnarray*}
	& y\in D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\} \subset R^N, \\
	& u\in U = \left\{ u_j \in  \left\{a_j, ..., b_j \right\}, 1\leq j \leq M \right\};
	\end{eqnarray*}
	i.e. this function has $N$ continuous and $M$ discrete parameters and reaches its minimum value at the point $(y',b)$.
	\item The coefficient
	\[
	C = 4 - \max \left\{ \phi(y,u) \right\}, \; y\in D, u \in U,
	\]
	is calculated. The maximum of the convex function $\phi(y,u)$ is achieved at one of the boundary points of the search domain; therefore, when the dimensionality of the problem is around 10, its calculation can be performed by the enumeration method. 
	\item  Multiextremal mixed-integer function
	\[
	\varphi(y,u) = \left(\psi(y) - \sum_{j=1}^M{u_j}\right)\left(C - \phi(y,u)\right)
	\]
	is formed. By construction, $\varphi(y,u)$ will reach the minimum value at the point $(y',b)$.

@@

The problems generated in our experiments had 5 discrete and 4 continuous parameters 
	\begin{eqnarray*}
	& y\in D = \left\{ -1 \leq y_j\leq 1, 1\leq j \leq 4 \right\} \subset R^4, \\
	& u\in U = \left\{ u_j \in  \left\{-1, -1/3, 1/3, 1 \right\}, 1\leq j \leq 5 \right\}.
	\end{eqnarray*}

In total, we generated and solved 100 9-dimensional mixed-integer problems of this type. In order to simulate the computational complexity inherent in applied optimization problems, the calculation of the function in all the experiments was complicated by additional calculations that did not change the form of the function and the location of its minima.
The accuracy of the search was equal to $\epsilon = 10^{-2}$. Computational experiments were carried out on the Lobachevsky supercomputer. The node of supercomputer included two Intel Sandy Bridge E5-2660 2.2 GHz CPUs and 64 Gb RAM.

@@

\begin{table}
	\caption{Average running time $T_{av}$ of the parallel algorithm with local tuning}
	\label{tab:3}
	\center
	\begin{tabular}{|c|c|c|c|}
		\hline	
	\diaghead{\theadfont Diag Column} { $N_{p}$}{$N_{t}$} & 1 & 4 & 8\\
